Towards Automated Merging of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-05-07 sattose/paper.tex
Ana

\begin{abstract}
Duplication in source code can have a major negative impact on the maintainability of source code, as it creates explicit dependencies between fragments of code. These explicit dependencies have been shown to often cause bugs, as a modification in one fragment might have consequences for the correctness of another. In this study, we look into the opportunities to automatically refactor these duplication problems for object-oriented programming languages. To do this, we propose a method to detect clones that are suitable for refactoring. This method focuses on taking into account the context and scope of clones, to be sure our refactoring improves the design and does not leave side effects after it is applied.

@@

\section{Introduction}
Duplication in source code is often seen as one of the most harmful types of technical debt. In Martin Fowler's ``Refactoring'' book \cite{fowler1999refactoring}, he exclaims that \textit{``Number one in the stink parade is duplicated code. If you see the same code structure in more than one place, you can be sure that your program will be better if you find a way to unify them.''}. In this research, we take a look at the challenges and opportunities in automatically refactoring duplicated code, also known as ``code clones''. The main goal is to improve the maintainability of the refactored code.

Refactoring is used to improve the quality-related attributes of a codebase (maintainability, performance, etc.) without changing the functionality. There are many methods that have been introduced to help with the process of refactoring \cite{fowler1999refactoring, wake2004refactoring}, that are integrated into most modern IDE's. However, most of these methods still require a manual assessment of where and when to apply them. Because of this, refactoring takes up a signification portion of the development process \cite{lientz1978characteristics, mens2004survey}, or does not happen at all \cite{mens2003refactoring}. For a large part, refactoring requires domain knowledge to do it right. However, there are also refactoring opportunities that are rather trivial and repetitive to execute. In this research, we investigate the extent to which code clones can be automatically refactored.

Code clones can be found anywhere in a codebase. The location of a clone in the code has an impact on how it can be refactored. Because of this, we will first look at where clones can be found. Using this information we can determine in which locations clones are found the most, on basis of which the refactoring will be prioritized. A duplicate part in a codebase does not always have to be an exact match with another part to be considered a clone. We will look at the definitions of different types of clones and the opportunities to refactor duplicate parts of code albeit not an exact match. We conduct our research on a large corpus of open source projects. We put the main focus on the Java programming language as refactoring opportunities feature paradigm and programming language dependent aspects~\cite{choi2011extracting}. However, most practices featured in this research will also be applicable to other object-oriented languages, like C\#.

For this research, we strive to improve upon the current state-of-the-art in clone refactoring \cite{fontana2015duplicated, alwaqfi2017refactoring} by building a clone refactoring tool that applies refactorings to a large percentage of clones found. The design decisions for this tool will be made on basis of data gathered from a large corpus of software systems. This way we strive to make the problem of duplication in source code easier to deal with.

\subsection{Background}
As code clones are seen as one of the most harmful types of technical debt, they have been studied very extensively. A survey by Roy et al. \cite{roy2007survey} states definitions for various important concepts in code clone research. In this survey, he mentions the concept ``clone pair'', which is \textit{a set of two code portions/fragments which are identical or similar to each other}. Furthermore, he defined ``clone class'' as \textit{the union of all clone pairs}. Apart from this, we use the definition ``clone instance'', which is a single code portion/fragment that is part of either a clone pair or clone class.

\subsubsection{Current clone refactoring tools}
A tool called DCRA (Duplicated Code Refactoring Advisor) looks into refactoring opportunities for clone pairs \cite{fontana2012duplicated}. This tool chooses to only focus on refactoring clone pairs because they argue that \textit{clone pairs are much easier to manage when considered singularly.} As intermediate steps, the authors measure a corpus of Java systems for some clone-related properties of the systems, like the relation (in terms of inheritance) between code fragments in a clone pair.

Another tool called Aries \cite{higo2004aries, higo2008metric} focuses on the detection of refactoring oriented clones. In this paper, the authors describe a few criteria by which a clone can be assessed to determine its suitability for refactoring. This tool looks however only at the possibility to merge clones, rather than whether clones should be merged (if they are actually harmful). Also, this tool only suggests refactorings and does not apply them.

There are many other publications that look into code clone refactoring \cite{alwaqfi2017refactoring, chen2018clone, koni2001scenario}. However, none of the publications describing a refactoring tool have published their source code or application for refactoring support. Furthermore, all of these tools only support a subset of all harmful clones that are found. Also, these publications/tools are limited to suggesting refactoring opportunities for clones found, rather than actually applying refactorings where suitable. Finally, all published approaches have limitations, such as false positives in their clone detection \cite{chen2018clone} or being limited to clone pairs \cite{higo2008metric}.

\subsubsection{Advantages of clone classes over clone pairs}\label{chap:cloneclasses}
Regarding clone detection, there is a lot of variability in literature whether clone pairs or clone classes should be detected. In this study we focus on clone classes, because of the advantages for refactoring. Clone pairs don’t provide a general overview of all entities containing the clones, with all their related issues and characteristics \cite{fontana2012duplicated}. Even though clone classes are harder to manage, they provide all information needed to plan a suitable refactoring strategy, since this way all instances of a clone are considered. Another issue involves clone grouping by pairs: single clone reference amount increases according to binomial coefficient formula (two clones form a pair, three clones form three pairs, four clones form six pairs, and so on), of which a heavy information redundancy follows \cite{fontana2012duplicated}.

\subsubsection{Clone types}
In a 2007 survey by Roy et al. \cite{roy2007survey} he defines four types of clones:\\
\textbf{Type 1:} Identical code fragments except for variations in whitespace (may be also variations in layout) and comments.\\
\textbf{Type 2:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
\textbf{Type 3:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout, and comments.\\
\textbf{Type 4:} Two or more code fragments that perform the same computation but implemented through different syntactic variants.

A higher type of clone means that it's harder to detect. It also makes the clone harder to refactor, as more transformations would be required. Higher clone types also become more disputable whether they actually indicate a harmful antipattern (as not every clone is harmful \cite{jarzabek2010clones, kapser2008cloning}).

@@

\subsection{Survey on Clone Detection Tools}
We conducted a short survey on (recent) clone detection tools that we could use to analyze refactoring possibilities. We chose a set of tools that are open source and can analyze either Java or Python. Then we chose four criteria by which we considered these tools: 
\begin{enumerate}
    \item \textbf{Should find clones in any context.} We want to perform an analysis on a set of projects. In this analysis we want to be able to get a full overview of cloning in the set of projects. Some tools only find clones in specific contexts, like only method-level clones. Because of that, we want to use a clone detection tool that is able to find clones in any context.
\item \textbf{Should detect clone classes in a number of example projects.} We have created a number of test projects\footnote{Our test projects to assess the validity of clone detection tools: \url{https://github.com/SimonBaars/CloneRefactor/tree/master/src/test/resources}} that we used to assess the validity of clone detection tools. On basis of this, we checked whether clone detection tools can correctly find clones in diverse contexts.
\item \textbf{Considers dependency graphs to be sure that this clone can be merged.} When detecting clones for refactoring purposes, it is important that clone instances are actually equal. Sometimes, to verify actual equality (not just textual equality), it is required to consider resolved symbols (this is described more elaborately in section \ref{chap:type1clones}). Because of this, we want to use a clone detection tool that can analyze such structures.
\item \textbf{Makes it possible to configure the way in which clones are detected (as in what to exclude from the detection) in a relatively straightforward way.} We want to be able to exclude expressions/statements from matching (more about our rationale in section \ref{chap:clonetypes}). To be able to do this, the tool needs to be able to recognize the meaning of certain tokens.
\end{enumerate}

The results of our survey are displayed in table \ref{table:dettools}.

@@

\subsection{CloneRefactor}
A 2016 survey by Gautam \cite{gautam2016various} focuses more on various techniques for clone detection. For our tool, we decided to combine AST- and Graph-based approaches for clone detection, similar to Scorpio \cite{higo2013revisiting, kamalpriya2017enhancing}. However, instead of building a dependency graph, we build a similarity graph of statements linking to similar statements. We decided to base our tool on the JavaParser library \cite{tomassetti2017javaparser}, as it supports rewriting the AST back to Java code and is compatible with all modern Java versions (Java 1-12). We collect each statement and declaration and compare those to find duplicates. This way we build a graph of each statement/declaration linking to each subsequent statement/declaration (horizontally) and linking to each of its duplicates (vertically). This is displayed in figure \ref{fig:clonerefactor}.

@@

On basis of this graph we detect clone classes. We challenge completed clone classes against the thresholds that are being used, and remove the clone classes that do not adhere to the thresholds.

@@

For the measurements in the next chapter we have chosen to apply the following thresholds:
\begin{itemize}
  \item \textbf{Number of statements/declarations:} 6
  \item \textbf{Number of tokens:} 10
  \item \textbf{Number of lines:} 6
\end{itemize}

\section{Addressing and solving problems with clone type definitions}\label{chap:clonetypes}
In this chapter, we will propose solutions for shortcomings in type 1, type 2 and type 3 clones \cite{roy2007survey} to increase the chance that we can merge the clone while improving the design. Type-4 clones are, because of the serious challenges involved in their detection and refactoring, out of the scope for this study.

\subsection{Type 1 clones} \label{chap:type1clones}
Type 1 clones are identical clone fragments except for variations in whitespace and comments. However, when two clone fragments are textually identical, it does not yet indicate that they are actually identical. Even when textually equal, method calls can refer to different methods, type declarations can refer to different types and even variables can be of a different type. This could invalidate a refactoring opportunity for such a code fragment. Because of that, we propose to:
\begin{itemize}
  \item \textbf{Compare the equality of the fully qualified method signature for method references.} If an identifier is fully qualified, it means we specify the full location of its declaration (e.g. \texttt{com.simonbaars.fruitgame.Apple} for an \texttt{Apple} object). This way we can validate whether two method references, like method calls, are actually equal. In the method signature, not only the fully qualified identifier of the method should be considered, but also the type of all its arguments. This way we can be sure that two potentially cloned method references do not point to overloaded variants (in a case that the data type of arguments is overloaded).
  \item \textbf{Compare the equality of the fully qualified identifier for type references.} This way we can be sure that two referenced types are actually equal, and that they are not just two types with the same name.
  \item \textbf{Compare the equality the fully qualified identifier for variable usages.} Two cloned lines might use a variable with the same name, but different types. This might pose serious challenges on refactoring, as the variables might not concern the same object or primitive. To check this, we need to track the declaration of variables and from this infer the fully qualified identifier of its type.
\end{itemize}

\subsection{Type 2 clones}
Type 2 clones, by definition, allow any change in identifiers, literals, types, layout, and comments. For refactoring purposes, this doesn't always make a lot of sense. If we allow any change in identifiers, literals, and types, we cannot distinguish between different variables, different types and different method calls anymore. This could render two methods that have an entirely different functionality as clones. Merging such clones, if possible at all, might only prove to be harmful.

Because of that, for this research, we have looked solving these problems with type 2 clones to be able to detect such clones that can and should be merged. Our definition ensures functional similarity by applying the following changes to type 2 clones:

\begin{itemize}
  \item \textbf{Considering types:} The definition of type 2 clones states that types should not be considered. We disagree because types can make a significant change to the meaning of a code segment and thus whether this segment should be considered a clone.
  \item \textbf{Having a distinction between different variables:} By the definition of type 2 clones, any identifiers would not be taken into account. We agree that a difference in identifiers may still result in a harmful clone, but we should still consider the distinction between different variables. For instance, if we call a method like this: \texttt{myMethod(var1, var2)}, or call this method like this: \texttt{myMethod(var1, var1)}. Even if the variables have the same type, the distinction between the variables is important to ensure the functionality is the same after merging.
  \item \textbf{Defining a threshold for variability in literals:} By the definition of type 2 clones any literals would not be taken into account. We agree, as when merging the clone (for instance by extracting a method), we can simply turn the literal into a method parameter. However, we would argue that thresholds matter here. How many literals may differ for the segment still to be considered a clone with another segment? We need to define a threshold to be sure that, by merging, we are not replacing a code fragment by a worse maintainable design.
  \item \textbf{Consider method call signatures and define a threshold for variability in method calls:} As type-2 clones allow changes in identifiers, also the names of called methods may vary. However, because of this, completely different methods can be called in cloned fragments as a result. This poses serious challenges on refactoring and makes it more disputable whether such a clone is actually harmful. This is because different method identifiers can describe a completely different functionality. Because of that, we recommend to keep considering the call signatures of cloned methods when they are compared. We can allow variability in the rest of method identifiers by passing the function as a parameter. To limit the amount of parameters required we also recommend defining a threshold for variability in method call expressions, so only a limited number of method calls can vary.
\end{itemize}

@@

\subsection{Next steps}
The next step will be to integrate our solutions for the problems with the clone types, as explained in section \ref{chap:clonetypes}, into our CloneRefactor tool. This way, we can run all scripts that we used for our measurements for these novel clone definitions. We are curious to see how it compares with the results we had so far.

>>>>

\begin{abstract}
Duplication in source code can have a major negative impact on the maintainability of source code, as it creates explicit dependencies between fragments of code. Such explicit dependencies often cause bugs. In this study, we look into the opportunities to automatically refactor these duplication problems for object-oriented programming languages. To do this, we propose a method to detect clones that are suitable for refactoring. This method focuses on the context and scope of clones, ensuring our refactoring improves the design and does not leave side effects after it is applied.

@@

\section{Introduction}
Duplication in source code is often seen as one of the most harmful types of technical debt. In Martin Fowler's ``Refactoring'' book \cite{fowler1999refactoring}, he claims that \textit{``Number one in the stink parade is duplicated code. If you see the same code structure in more than one place, you can be sure that your program will be better if you find a way to unify them.''}. 
% In this research, we take a look at the challenges and opportunities in automatically refactoring duplicated code, also known as ``code clones''. The main goal is to improve the maintainability of the refactored code.

Refactoring is used to improve the quality-related attributes of a codebase (maintainability, performance, etc.) without changing the functionality. Many methods were introduced to aid the process of refactoring~\cite{fowler1999refactoring, wake2004refactoring}, and are integrated into most modern IDE's. However, most of these methods still require a manual assessment of where and when to apply them. This means refactoring is either a significant part of the development process~\cite{lientz1978characteristics, mens2004survey}, or does not happen at all~\cite{mens2003refactoring}. For a large part, proper refactoring requires domain knowledge. However, there are also refactoring opportunities that are rather trivial and repetitive to execute. In this research, we investigate the extent to which code clones can be automatically refactored.

Code clones can be found anywhere in a codebase. The location of a clone in the code has an impact on how it can be refactored. Therefore, we first look at where and how often clones can be found, enabling the prioritization of refactoring opportunities.
% Using this information we can determine in which locations clones are found the most, on basis of which the refactoring will be prioritized. 
Furthermore, a duplicate fragment in a codebase does not always have to be an exact match with another fragment to be considered a clone. Therefore, we also analyse the impact of the different definitions of clone types on refactoring opportunities.
% We look at the definitions of different types of clones and the opportunities to refactor duplicate parts of code albeit not an exact match.

We conduct our research on a large corpus of open source projects. We focus mainly on the Java programming language as refactoring opportunities feature paradigm and programming language dependent aspects~\cite{choi2011extracting}. However, most practices featured in this research will also be applicable to other object-oriented languages, like C\#.

In this research, we strive to improve upon the current state-of-the-art in clone refactoring \cite{fontana2015duplicated, alwaqfi2017refactoring} by building a clone refactoring tool that automatically applies refactorings to a large percentage of clones found. The design decisions for this tool are made on basis of data gathered from a large corpus of software systems.

\section{Background}
As code clones are seen as one of the most harmful types of technical debt, they have been studied extensively. A survey by Roy et al.~\cite{roy2007survey} states definitions of important concepts in code clone research. For instance, ``clone pair''is defined as \textit{a set of two code portions/fragments which are identical or similar to each other}; ``clone class'' as \textit{the union of all clone pairs}; ``clone instance'' as a single code portion/fragment that is part of either a clone pair or clone class.
\subsection{Advantages of clone classes over clone pairs}\label{chap:cloneclasses}
Regarding clone detection, there is a lot of variability in literature whether clone pairs or clone classes should be detected. In this study we focus on clone classes, because of the advantages for refactoring. Clone pairs don not provide a general overview of all entities containing the clones, with all their related issues and characteristics \cite{fontana2012duplicated}. Although clone classes are harder to manage, they provide all information needed to plan a suitable refactoring strategy, since this way all instances of a clone are considered. Another issue involves clone grouping by pairs: single clone reference amount increases according to binomial coefficient formula (two clones form a pair, three clones form three pairs, four clones form six pairs, and so on), of which a heavy information redundancy follows \cite{fontana2012duplicated}.

\subsection{Clone types}
In a 2007 survey by Roy et al. \cite{roy2007survey} he defines four types of clones:\\
\textbf{Type 1:} Identical code fragments except for variations in whitespace (may be also variations in layout) and comments.\\
\textbf{Type 2:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
\textbf{Type 3:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout, and comments.\\
\textbf{Type 4:} Two or more code fragments that perform the same computation but implemented through different syntactic variants.

A higher type of clone means that it is harder to detect. It also makes the clone harder to refactor, as more transformations would be required. Higher clone types also become more disputable whether they actually indicate a harmful antipattern (as not every clone is harmful \cite{jarzabek2010clones, kapser2008cloning}).
\subsection{Related work in clone refactoring tools}
The Duplicated Code Refactoring Advisor (DCRA) looks into refactoring opportunities for clone pairs \cite{fontana2012duplicated}. This tool only focuses on refactoring clone pairs, the authors arguing that \textit{clone pairs are much easier to manage when considered singularly.} As intermediate steps, the authors measure a corpus of Java systems for some clone-related properties of the systems, like the relation (in terms of inheritance) between code fragments in a clone pair.

Aries \cite{higo2004aries, higo2008metric} focuses on the detection of refactoring oriented clones. The authors describe a \todo{same criteria as you? different?} few criteria by which a clone can be assessed to determine its suitability for refactoring. However, \todo{can you be more precise?} this tool looks only at the possibility to merge clones, rather than whether clones should be merged (if they are actually harmful). Aries only suggests refactorings and does not apply them.

There are many other research efforts looking into code clone refactoring \cite{alwaqfi2017refactoring, chen2018clone, koni2001scenario}. However, 
% none of the publications describing a refactoring tool have published their source code or application for refactoring support. Furthermore, 
all of these tools only support a subset of all harmful clones that are found. Also, these tools are limited to suggesting refactoring opportunities, rather than actually applying refactorings where suitable. Finally, all published approaches have limitations, such as false positives in their clone detection \cite{chen2018clone} or being limited to clone pairs \cite{higo2008metric}.

@@

\subsection{Survey on Clone Detection Tools}
We conducted a short survey on (recent) clone detection tools that we could use to analyze refactoring possibilities. The results of our survey are displayed in table~\ref{table:dettools}. We chose a set of tools that are open source and can analyze either Java or Python. Then we chose four criteria by which we considered these tools: 
\begin{enumerate}
    \item \textbf{Should find clones in any context.} We want to perform an analysis on a set of projects. In this analysis we want to be able to get a full overview of cloning in the set of projects. Some tools only find clones in specific contexts, like only method-level clones. Because of that, we want to use a clone detection tool that is able to find clones in any context.
\item \textbf{Should detect clone classes in a number of example projects.} We have created a number of test projects\footnote{Our test projects to assess the validity of clone detection tools: \url{https://github.com/SimonBaars/CloneRefactor/tree/master/src/test/resources}} that we used to assess the validity of clone detection tools. On basis of this, we checked whether clone detection tools can correctly find clones in diverse contexts.
\item \textbf{Considers dependency graphs to be sure that this clone can be merged.} When detecting clones for refactoring purposes, it is important that clone instances are actually equal. Sometimes, to verify actual equality (not just textual equality), it is required to consider resolved symbols (this is described more elaborately in section \ref{chap:type1clones}). Because of this, we want to use a clone detection tool that can analyze such structures.
\item \textbf{Makes it possible to configure the way in which clones are detected (as in what to exclude from the detection) in a relatively straightforward way.} We aim to exclude expressions/statements from matching (more about our rationale in section~\ref{chap:clonetypes}). To achieve this, the tool needs to be able to recognize the meaning of certain tokens.
\end{enumerate}

@@

\subsection{CloneRefactor}
A 2016 survey by Gautam \cite{gautam2016various} focuses more on various techniques for clone detection. We decided to combine AST- and Graph-based approaches for clone detection, similar to Scorpio \cite{higo2013revisiting, kamalpriya2017enhancing}. However, instead of building a dependency graph, we build a similarity graph of statements linking to similar statements. The graph built by CloneRefactor is shown in figure \ref{fig:clonerefactor}.

We decided to base our tool on the JavaParser library \cite{tomassetti2017javaparser}, as it supports rewriting the AST back to Java code and is compatible with all modern Java versions (Java 1-12). We collect each statement and declaration and compare those to find duplicates. This way we build a graph of each statement/declaration linking to each subsequent statement/declaration (horizontally) and linking to each of its duplicates (vertically). On basis of this graph we detect clone classes.

We challenge completed clone classes against the thresholds that are being used, and remove the clone classes that do not adhere to the thresholds.

@@

@@

The measurements in our study use the following thresholds:
\begin{itemize}
  \item \textbf{Number of statements/declarations:} 6
  \item \textbf{Number of tokens:} 10
  \item \textbf{Number of lines:} 6
\end{itemize}

\section{Addressing problems with clone type definitions}\label{chap:clonetypes}
We propose solutions for shortcomings in type 1, type 2 and type 3 clones~\cite{roy2007survey} to increase the chance that we can merge the clone while improving the design. Due to the serious challenges involved in their detection and refactoring, type 4 clones are not considered in this study.

\subsection{Type 1 clones} \label{chap:type1clones}
Type 1 clones are identical clone fragments except for variations in whitespace and comments. However, when two clone fragments are textually identical, it does not yet indicate that they are actually identical. Even when textually equal, method calls can refer to different methods, type declarations can refer to different types and even variables can be of a different type. This could invalidate a refactoring opportunity for such a code fragment. Therefore, we propose to:
\begin{itemize}
  \item \textbf{Compare the equality of the fully qualified method signature for method references.} If an identifier is fully qualified, it means we specify the full location of its declaration (e.g. \texttt{com.simonbaars.fruitgame.Apple} for an \texttt{Apple} object). This way we can validate whether two method references, like method calls, are actually equal. In the method signature, not only the fully qualified identifier of the method should be considered, but also the type of all its arguments. This way we can be sure that two potentially cloned method references do not point to overloaded variants (in a case that the data type of arguments is overloaded).
  \item \textbf{Compare the equality of the fully qualified identifier for type references.} This way we can be sure that two referenced types are actually equal, and that they are not just two types with the same name.
  \item \textbf{Compare the equality the fully qualified identifier for variable usages.} Two cloned lines might use a variable with the same name, but different types. This might pose serious challenges on refactoring, as the variables might not concern the same object or primitive. To check this, we need to track the declaration of variables and from this infer the fully qualified identifier of its type.
\end{itemize}

\subsection{Type 2 clones}
By definition, type 2 clones allow any change in identifiers, literals, types, layout, and comments. For refactoring purposes, this does not always make a lot of sense. If we allow any change in identifiers, literals, and types, we cannot distinguish between different variables, different types and different method calls anymore. This could render two methods that have an entirely different functionality as clones. Merging such clones might only prove to be harmful.

We tackle these problems with type 2 clones to be able to detect such clones that can and should be merged. Our definition ensures functional similarity by applying the following changes to type 2 clones:

\begin{itemize}
  \item \textbf{Considering types:} The definition of type 2 clones states that types should not be considered. We disagree because types can make a significant change to the meaning of a code segment and thus whether this segment should be considered a clone.
  \item \textbf{Having a distinction between different variables:} By the definition of type 2 clones, any identifiers would not be taken into account. We agree that a difference in identifiers may still result in a harmful clone, but we should still consider the distinction between different variables. For instance, if we call a method like this: \texttt{myMethod(var1, var2)}, or call this method like this: \texttt{myMethod(var1, var1)}. Even if the variables have the same type, the distinction between the variables is important to ensure the functionality is the same after merging.
  \item \textbf{Defining a threshold for variability in literals:} By the definition of type 2 clones any literals would not be taken into account. We agree, as when merging the clone (for instance by extracting a method), we can simply turn the literal into a method parameter. However, we would argue that thresholds matter here. How many literals may differ for the segment still to be considered a clone with another segment? We need to define a threshold to be sure that, by merging, we are not replacing a code fragment by a worse maintainable design.
  \item \textbf{Consider method call signatures and define a threshold for variability in method calls:} As type-2 clones allow changes in identifiers, also the names of called methods may vary. However, because of this, completely different methods can be called in cloned fragments as a result. This poses serious challenges on refactoring and makes it more disputable whether such a clone is actually harmful. This is because different method identifiers can describe a completely different functionality. Therefore, we suggest considering the call signatures of cloned methods when they are compared. We can allow variability in the rest of method identifiers by passing the function as a parameter. To limit the amount of parameters required we also recommend defining a threshold for variability in method call expressions, so only a limited number of method calls can vary.
\end{itemize}

@@

\subsection{Next steps}
The next step is to integrate our solutions for the problems related to clone types into our CloneRefactor tool. This way, we can perform our experiments for these novel clone definitions. We are curious to see how it compares with the results we had so far.
